Analysing the three-dimensional structure of \em{P. falciparum}

### 2017-07-03 doc/manuscript/paper.tex
More on publicly available softwares
VE models

\begin{itemize}
\item All beads lie in a spherical nucleus centered on the origin and of a
certain size.
\item Two adjacent beads must not be too far apart. Leveraging the work of
\citet{berger}, we assume that $b^\text{max} = 91~nm$
\end{itemize}

Note that in practice, the constraints are fulfilled naturally by the data,
and thus can be dropped.

@@

\subsubsection{Volume exclusion models}

>>>>

\begin{itemize}
\item All beads lie in a spherical nucleus centered on the origin and of a
certain size.
\item Two adjacent beads must not be too far apart. Leveraging the work of
\citet{berger:high TOVERIFY}, we assume that $b^\text{max} = 91~nm$
\end{itemize}

Note that in practice, the constraints are fulfilled naturally by the data,
and thus can be dropped. In addition of drastically reducing the computation
time, this allows to use generic publicly available software such as chromSDE
(which implements a variant of the model defined here), or Pastis-MDS (which
implements exactly the unconstrained model defined here).

@@

\subsubsection{Volume exclusion models}
blha

\citet{tjong:physical} showed \textit{S. cerevisiae}'s structure can be mostly
explained by a large set of constrained yet random population of structures
following a simple volume exclusion model. We repeated the experiment on {\em
P. falciparum}, and showed that, despite recovering similar results on {\em S.
cerevisiae}, the same set of constraints is not sufficient to explain {\em P.
falciparum}'s Hi-C contact map.

Briefly, let us recall the methodology presented by \citet{tjong:physical}. We
construct a population of three-dimensional structures by modeling chromosomes
as random configuration of beads-on-a-string, subjected to the following constraints.

\begin{itemize}
\item \textbf{Adjacent Beads Constraints} Two adjacent beads spaced 3.2kb apart are constrained to be 30nm apatr.
\item \textbf{Volume Exclusion Constraints} Each pairs of beads are spaced at minimum XX apart
\item \textbf{Nucleus Constraint} All beads lie in a spherical nucleus of specific
radius (XXX)
\item \textbf{Centromeres Constraints} Centromeres are localized in a small sphere of
50nm abutting the nuclear envelop.
\item \textbf{Telomere Constraints} Telomeres are located at most 50nm from the nuclear envelop.
\end{itemize}

\citet{tjong:physical} then formulates an optimization problem that includes
in addition to all the aforementioned constraints a penalty term on three
adjacent beads accounting for chromatin stiffness.

$$
\frac{1}{2} FIXME
$$
